Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-09-23 AO_bondedSi.tex
having problems with latex-diff, something about bib file

We can treat a small Si$-$Si interface gap between two almost-bonded silicon parts as a low-Finesse Fabry-P\'{e}rot etalon\cite{2007fuph.book.....S}.  The key property of an etalon is that it has a cavity enclosed between two smooth and parallel reflective surfaces where the requirements for smoothness and parallelism depend on the reflective finesse of the cavity.  For the narrow air gaps we consider here and for the modest reflectivity of a Si-vacuum interface, most gaps at Si$-$Si bonds will form effective etalons over most of their area.  The transmission through a Fabry-P\'{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We compute the Si$-$vacuum interface reflectivity, which is a modest function of wavelength, through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, where $T$ is temperature.  We adopt room temperature values through this article.  We drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ and the coefficient of finesse $F(\lambda, T) \rightarrow F$ for clarity.  The computation is simply Fresnel's law at normal incidence:

@@

We define the coefficient of finesse\cite{2007fuph.book.....S}, $F$ (Equation \ref{Eq:coeffF}), in the customary way to encapsulate the Fabry-P\'{e}rot etalon's dependence on reflectivity.  The right panel of Figure \ref{figSiIndexFinesse} shows the coefficient of finesse as a function of wavelength.  In this work, we assume transmission is at normal incidence and the refractive index of the gap is 1.0.  Si absorbs negligibly longward of $\lambda$ = 1250 nm, which we verified by comparing the transmission of Si reference samples of different thicknesses (Figure \ref{figSiAbsorbfig}).  We measured the ratio of transmissions of a 0.5 mm thick double side polished Si wafer and a 3.0 mm Si puck.  Figure \ref{figSiAbsorbfig} verifies a key assumption that we make when comparing the transmission of scrap Si of different provenance and thickness: double side polished 3 mm thick Si pucks and 0.5 mm thick Si wafers have indistinguishable transmission at the $<0.2$\% level long-ward of $1250\;$nm.  The Si refractive index is indistinguishable from sample to sample for the wavelength ranges we care about- the non-absorbing wavelengths greater than about 1250 nm.  \cite{2006SPIE.6273E..77F} cites the wide variety of values for refractive index from the literature as evidence that batch-specific Si should be used as a reference for cases in which absolute accuracy greater than $\pm5\times10^{-3}$ is desired.  An absolute deviation of $\pm5\times10^{-3}$ in refractive index corresponds to a Fresnel transmission difference of about 0.2\%, which is comparable to our measurement uncertainty.  In the next subsection we work out the wavelength dependent transmission for the air etalon\footnote{A note on nomenclature- we use the term \emph{gap} for the physical structure, and \emph{etalon} for the model of that structure.}

@@

%New prose here:
At this stage, \emph{any} regression technique can be employed to compare the model to data.  Least squares regression, and other popular methods can be applied, for example.  However, since least squares regression assumes zero bias term, we elected to apply a Gaussian process regression technique that can handle biased measurements.  Given the relatively small bias amplitude we measured, least squares regression and Gaussian process regression would likely yield similar solutions for the gap size, but least squares regression would drastically underestimate the uncertainty associated with the gap size\citep{DFMgp}.

@@

MGS acknowledges support from Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA ACT grant NNX12AC31G.  The authors thank Amanda Turbyfill, Mike Pavel, and Carleen Boyer for assistance with IR imaging and specroscopy.  MGS thanks the organizers and participants of the \emph{Astro Data Hack Week} (2014), especially Dan Foreman-Mackey for sharing tutorials and code for implementing the Gaussian process technique.  This research has made use of NASA's Astrophysics Data System.  Many of the figures in the paper were made with Matplotlib \citep{Hunter:2007} in IPython Notebooks \citep{PER-GRA:2007}.  The Notebooks with complete version history are available on GitHub\footnote{\url{https://github.com/Echelle/AO_bonding_paper}}.

>>>>

We can treat a small Si$-$Si interface gap between two almost-bonded silicon parts as a low-Finesse Fabry-P\'{e}rot etalon\cite{2007fuph.book.....S}.  The key property of an etalon is that it has a cavity enclosed between two smooth and parallel reflective surfaces where the requirements for smoothness and parallelism depend on the reflective finesse of the cavity.  For the narrow air gaps we consider here and for the modest reflectivity of a Si-vacuum interface, most gaps at Si$-$Si bonds will form effective etalons over most of their area.  The transmission through a Fabry-P\'{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We compute the Si$-$vacuum interface reflectivity, which is a modest function of wavelength, through the refractive index of Silicon, $n(\lambda, T)$, where $T$ is temperature \cite{2006SPIE.6273E..77F}.  We adopt room temperature values through this article.  We drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ and the coefficient of finesse $F(\lambda, T) \rightarrow F$ for clarity.  The computation is simply Fresnel's law at normal incidence:

@@

We define the coefficient of finesse\cite{2007fuph.book.....S}, $F$ (Equation \ref{Eq:coeffF}), in the customary way to encapsulate the Fabry-P\'{e}rot etalon's dependence on reflectivity.  We calculate a coefficient of finesse in the range 2.5$-$2.6, depending on wavelength.  In this work, we assume transmission is at normal incidence and the refractive index of the gap is 1.0.  Si absorbs negligibly longward of $\lambda$ = 1250 nm, which we verified by comparing the transmission of Si reference samples of different thicknesses (Figure \ref{figSiAbsorbfig}).  We measured the ratio of transmissions of a 0.5 mm thick double side polished Si wafer and a 3.0 mm Si puck.  Figure \ref{figSiAbsorbfig} verifies a key assumption that we make when comparing the transmission of scrap Si of different provenance and thickness: double side polished 3 mm thick Si pucks and 0.5 mm thick Si wafers have indistinguishable transmission at the $<0.2$\% level long-ward of $1250\;$nm.  The Si refractive index is indistinguishable from sample to sample for the wavelength ranges we care about- the non-absorbing wavelengths greater than about 1250 nm.  \cite{2006SPIE.6273E..77F} cites the wide variety of values for refractive index from the literature as evidence that batch-specific Si should be used as a reference for cases in which absolute accuracy greater than $\pm5\times10^{-3}$ is desired.  An absolute deviation of $\pm5\times10^{-3}$ in refractive index corresponds to a Fresnel transmission difference of about 0.2\%, which is comparable to our measurement uncertainty.  In the next subsection we work out the wavelength dependent transmission for the air etalon\footnote{A note on nomenclature- we use the term \emph{gap} for the physical structure, and \emph{etalon} for the model of that structure.}

@@

%New prose here:
At this stage, \emph{any} regression technique can be employed to compare the model to data.  Least squares regression, and other popular methods can be applied, for example.  However, since least squares regression assumes zero bias term, we elected to apply a Gaussian process regression technique that can handle biased measurements.  Given the relatively small bias amplitude we measured, least squares regression and Gaussian process regression would likely yield similar solutions for the gap size, but least squares regression would drastically underestimate the uncertainty associated with the gap size\cite{DFMgp}.

@@

MGS acknowledges support from Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA ACT grant NNX12AC31G.  The authors thank Amanda Turbyfill, Mike Pavel, and Carleen Boyer for assistance with IR imaging and specroscopy.  MGS thanks the organizers and participants of the \emph{Astro Data Hack Week} (2014), especially Dan Foreman-Mackey for sharing tutorials and code for implementing the Gaussian process technique.  This research has made use of NASA's Astrophysics Data System.  Many of the figures in the paper were made with Matplotlib \cite{Hunter:2007} in IPython Notebooks \cite{PER-GRA:2007}.  The Notebooks with complete version history are available on GitHub\footnote{\url{https://github.com/Echelle/AO_bonding_paper}}.
